\documentclass[a4paper,12pt]{article}
\usepackage[margin=1.5cm]{geometry}
\pagestyle{empty}
\begin{document}
  \begin{flushleft}
    \small
    Submittees: \\
    Gurmukh Singh (008)\\
    Gaurav Hooda (033)\\
    Dushyant Kumar (067)
  \end{flushleft}
  \vspace{-0.94in}
  \begin{flushright}
    \small
    Submitted to:\\
    Prof. Shubhani
  \end{flushright}
  \begin{center}
    \Large{\textbf{CRISPR: Shaping a New Tomorrow}}\\
    \large{Understanding the Potential of CRISPR}
  \end{center}
  \begin{flushright}
    \small
    Subject: OOPC
  \end{flushright}
  \hrule
  \section{Introduction}
  \subsection{What is CRISPR}
  CRISPR stands for Clustered Regualrly Interspaced Short Palindromic Repeats. It is a revolutionary gene-editing tool that allows precise modification of DNA, offering unprecedented potential for scientific and medical advancement. 
  \subsection{How does CRISPR work}
  \begin{enumerate}
    \item Scientists take a snippet of RNA (guide RNA or gRNA) and pair it with a Cas protein (usually Cas9).
    \item The guide RNA leads the Cas protein to the target location on the subject's DNA.
    \item The Cas protein cuts the DNA at this location.
    \item The cell then can repair the broken DNA in 2 ways:
      \begin{enumerate}
        \item By gluing the two ends back together. This can sometimes introduce or remove new nucleotides which can alter the gene.
        \item By using a piece of donor DNA as a template to insert the desired DNA modification
      \end{enumerate}
  \end{enumerate}
  \section{The Possibilities}
  This technology has the potential to revolutionize many fields including Medicine, Agriculture and even Biofuels.
  \subsection{Examples of the Uses}
  \begin{enumerate}
    \item Treatment of a lot of ailments that occur because of genetic mutations. For Example:
      \begin{itemize}
        \item Cystic Fibrosis
        \item Sickle cell anemia
      \end{itemize}
    \item The Development of Crops with better resistance to pests and diseases.
    \item Creation of biofuels which are more efficient and sustainable.
    \item Choosing the characteristics of our offsprings.
      \begin{itemize}
        \item We can choose the traits our children. Like eye color, height etc.
        \item We can make them immune to specific diseases from birth. 
      \end{itemize}
  \end{enumerate}
  \section{The Concerns}
  \subsection{Germline editing concerns}
  Germline editing with CRISPR raises complex questions about heritability, human enhancement and long-term consequences, demanding thoughtful deliberation.
  \subsection{Unintended Consequences}
  \subsection{Ethical Concerns}
\end{document}

